Include a header paragraph specific to your product here. Customer requirements are those required features and functions specified for and by the intended audience for this product. This section establishes, clearly and concisely, the "look and feel" of the product, what each potential end-user should expect the product do and/or not do. Each requirement specified in this section is associated with a specific customer need that will be satisfied. In general Customer Requirements are the directly observable features and functions of the product that will be encountered by its users. Requirements specified in this section are created with, and must not be changed without, specific agreement of the intended customer/user/sponsor.

\subsection{GPS}
\subsubsection{Description}
As part of the autonomous navigation system, the GPS would provide coordinate data which would allow the program to know the position of the longboard which would be used to draw vectors to aid with navigation to a target coordinate.
\subsubsection{Source}
The GPS built into the phone will be used to get the current location of the longboard.
\subsubsection{Constraints}
The GPS coordinates provided by the phone should be precise without jumping from one value to another too much.
\subsubsection{Standards}
Conforms to the standard Global Positioning System.
\subsubsection{Priority}
High

\subsection{Remote}
\subsubsection{Description}
Instead of having a separate remote, a free-to-download app will be made available which can be used to summon the board, enable the follow-me feature, and control the speed of the wheels. The app currently uses React as the framework of choice for the front-end and is hosted publicly on Netlify. It uses sockets for communication, but a better approach we found is Bluetooth which would make the process of data transfer very simple and easy. The app  will soon be changed to using React Native to support both Android and IOS. The reason for this is to ensure full compatibility without having to worry about browser versions.
\subsubsection{Source}
Native Android and IOS application making use of Bluetooth to communicate with the longboard.
\subsubsection{Constraints}
Since the rider of the longboard will be going quite fast, the transmission of data needs to be reduced as much as possible. Latency should be minimized.
\subsubsection{Standards}
Bluetooth 4.0/5.0 for maximum compatibility.
\subsubsection{Priority}
High
