The product will be shipped pre-assembled which would include the turning mechanism, camera, and Jetson already screwed onto a standard longboard. The only thing not plugged in would be the batteries which the user has to connect themselves. The firmware for the product will come pre-installed where the user would only be required to pair the device with the mobile app to make use of it. An ankle bracelet with ArUco Tags for the follow me feature and a power supply for charging the batteries would also be included as part of the purchase.

\subsection{Requirement Name}
\subsubsection{Description}
Due to the nature of the product, the main point of failure is the turning mechanism which needs to be protected using bubble wrap with zip ties holding it in place to prevent it from shaking during shipping. Anything electrical which might not be inside of an enclosure will be contained inside of ant-static bags to prevent static from killing the parts. The Ankle bracelet will be packaged separately in a hard casing to prevent it from bending or being compressed during shipping. The batteries would come packaged inside of an insulated bag alongside the power supply. All the components would be placed inside of the delivery box which would have dedicated sections for each part.
\subsubsection{Source}
These are some of the locations from which the parts are being sourced:\\
1. Adafruit\\
2. Amazon\\
3. eBay
\subsubsection{Constraints}
One of the major constraints is to make sure that the board does not move around too much whilst shipping as it contains sensitive components which might get chipped off in a scenario where a screw comes loose, and the PCB hits the inside of the casing. Also, the shipping environment should have a fairly constant temperature as electrical components are heavily affected by temperature which might cause the parts to degrade. The latter scenario is an extreme case.
\subsubsection{Standards}
The shipment should be handled with care and not thrown around which moving from one shipment container to another.
\subsubsection{Priority}
High

\subsection{Dampeners}
\subsubsection{Description}
Excessive vibrations within the electronic housing can cause destructive resonance and render the board non-functional. In order to absorb these vibrations foam dampeners will be installed around all essential parts of the internal components.
\subsubsection{Source}
This requirement comes from the hardware engineers responsible for designing the internal components.
\subsubsection{Constraints}
Foam that is rigid enough to absorb vibrations caused by fast movement over uneven terrain but will not compress enough to cause damage to the internals.
\subsubsection{Standards}
No standards will be used.
\subsubsection{Priority}
High
